---
title: "Basic Course Template CUNY SPS Master's of Data Science"
output: github_document
date: "`r paste(params$semester, params$year)`"
geometry: margin=0.75in
editor_options: 
  chunk_output_type: console
params:
  semester: "Fall"
  year: "2021"
---


```{r setup, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
# Setup code

```

**Instructor Name:** INSTUCTOR NAME  
**Instructor Email:** [EMAIL](mailto:EMAIL)  
**Class Meetup:** TBD
**Office Hours:** Friday 12pm to 1pm & by appointment  
**Degree Program:** M.S. in Data Science  
**Credits:** 3 graduate credits  
**Prerequisites:** None  
**Type of Course:** Required course  

### Course Description

### Course Learning Outcomes:

By then end of the course, students should be able to:

* Learn some new Data Science skills

### Program Learning Outcomes addressed by the course:


### Grading

* Homework (X%)
* Labs (X%)
* Project (X%)
* Participation (X%)

```{r, child='includes/grade_distribution.md'}
```

### Schedule


```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, results='asis'}
source('R/build_schedule.R')
build_schedule('Schedule.csv', year = params$year, semester = params$semester)
```




```{r, child='includes/accessibility.md'}
```

```{r, child='includes/online_etiquette.md'}
```

```{r, child='includes/academic_integrity.md'}
```

```{r, child='includes/support_services.md'}
```
