---
title: "Basic Course Template CUNY SPS Master's of Data Science"
output: github_document
geometry: margin=0.75in
editor_options: 
  chunk_output_type: console
always_allow_html: true
---


```{r setup, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
# Setup code
semester <- "Fall"
year <- 2021
```

**Instructor Name:** INSTUCTOR NAME  
**Instructor Email:** [EMAIL](mailto:EMAIL)  
**Class Meetup:** TBD
**Office Hours:** by appointment  
**Degree Program:** M.S. in Data Science  
**Credits:** 3 graduate credits  
**Prerequisites:** None  
**Type of Course:** Required course  

### Course Description

### Course Learning Outcomes:

By then end of the course, students should be able to:

* Learn some new Data Science skills

### Program Learning Outcomes addressed by the course:


### Grading

* [Homework](#homework) (X%)
* Labs(#labs) (X%)
* [Project](/project/project.md) (X%)
* Participation (X%)

```{r, child='includes/grade_distribution.md'}
```

#### Homework {#homework}

1. [Homework 1](homework/Homework1.pdf) ([template](homework/Homework1.Rmd))

#### Labs {#labs}

1. [Lab 1](labs/Lab1/Lab1_intro_to_r.pdf) ([template](/labs/Lab1/Lab1_intro_to_r.Rmd))

#### Project




### Schedule


```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, results='asis'}
source('R/build_schedule.R')
build_schedule('Schedule.csv', year = year, semester = semester)
```




```{r, child='includes/accessibility.md'}
```

```{r, child='includes/online_etiquette.md'}
```

```{r, child='includes/academic_integrity.md'}
```

```{r, child='includes/support_services.md'}
```
